---
title: "freesearcheR analysis results"
date: today
format: docx
author: freesearcheR Tool
toc: false
execute: 
  echo: false
params:
  data.file: NA
---

```{r}
#| message: false
#| warning: false
# if (!requireNamespace("gtsummary")){
#   install.packages("gtsummary")
#   } else {
#   library(gtsummary)
#   }
# 
# if (!requireNamespace("gt")){
#   install.packages("gt")
#   } else {
#   library(gt)
#   }
# 
# if (!requireNamespace("readr")){
#   install.packages("readr")
#   } else {
#   library(readr)
#   }
# requireNamespace("gtsummary")
# requireNamespace("gt")
# require(gt)
# require(flextable)
# if (!requireNamespace("readr")){
#   install.packages("readr")
# }
web_data <- readr::read_rds(file = params$data.file)
# library(gt)
# library(flextable)
# library(freesearcheR)
```

## Introduction

Research should be free and open with easy access for all. The freesearcheR tool attempts to help lower the bar to participate in contributing to science by making guided data analysis easily accessible in the web-browser.

## Methods

Analyses were conducted in the *freesearcheR* data analysis web-tool based on R version 4.4.1.

## Results

Below are the baseline characteristics.

{{< include _table1.md >}}

Below are results from the univariable and multivariable regression analyses.


```{r}
gtsummary::tbl_summary(mtcars,by=cyl)
```

## Discussion

Good luck on your further work!
