---
format: 
  html:
    embed-resources: true
title: "freesearcheR analysis results"
date: today
author: freesearcheR Tool
toc: true
execute: 
  echo: false
params:
  data.file: NA
---

```{r setup}
web_data <- readr::read_rds(file = params$data.file)
library(gtsummary)
library(gt)
library(flextable)
# library(freesearcheR)
```

## Introduction

Research should be free and open with easy access for all. The freesearcheR tool attempts to help lower the bar to participate in contributing to science by making guided data analysis easily accessible in the web-browser.

## Methods

Analyses were conducted in R version `r paste(version["major"],version["minor"],sep=".")`.

## Results

Below is the baseline characteristics plotted.

```{r}
#| label: tbl-baseline
#| tbl-cap: Baseline characteristics of included data
web_data$table1 |> 
  gtsummary::as_flex_table() |> 
  flextable::set_table_properties(width = 1, layout = "autofit")
```

Here are the results from the `r web_data$regression$options$descr`.

```{r}
#| label: tbl-regression
#| tbl-cap: Regression analysis results
web_data$regression$table|> 
  gtsummary::as_flex_table() |> 
  flextable::set_table_properties(width = 1, layout = "autofit")
```

## Discussion

Good luck on your further work!
