---
title: "Data types"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data-types}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup}
library(FreesearchR)
```

## A clinical data class

Traditionally in *R*, data is identified by classes, like numeric, integer, double, logical, factor etc. These classes can be a little confusing from a clinical or operational standpoint. In the ***FreesearchR*** app, these classes has been simplified and modified to the following data types, that are assigned on a prioritised order like the following:

```{r echo = FALSE, eval = TRUE}
data_types() |> purrr::imap(\(.x,.i){
  dplyr::bind_cols("type"=.i,.x,.name_repair = "unique_quiet")
  }) |> dplyr::bind_rows() |> 
  setNames(c("Data type","Description","Data classes included")) |> 
  kableExtra::kable()
```

Categorising data in this way makes sense when making choices on how to evaluate and analyse data. This is used throughout the ***FreesearchR*** app to simplify data handling.
