---
title: "On visuals"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{visuals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup}
library(FreesearchR)
```

## Basic visualisations

The goal of ***FreesearchR*** is to keep things simple. Visuals can get very complicated. We provide a selection of plots, that helps visualise typical clinical and will be enough for most use cases, and for publishing to most journals.

If you want to go further, have a look at these sites with suggestions and sample code for data plotting:

-   [*R* Charts](https://r-charts.com/): Extensive gallery with great plots

-   [*R* Graph gallery](https://r-graph-gallery.com/): Another gallery with great graphs

-   [graphics principles](https://graphicsprinciples.github.io/): Easy to follow recommendations for clear visuals. 


### Available plots

Below are the available plot types listed.

```{r echo = FALSE, eval = TRUE}
c("continuous", "dichotomous", "categorical") |> 
  lapply(\(.x){
    dplyr::bind_cols(
      dplyr::tibble("Data type"=.x),
      supported_plots() |> 
      lapply(\(.y){
        if (.x %in% .y$primary.type){
          .y[c("descr","note")]|> dplyr::bind_cols()
        }
})|> 
  dplyr::bind_rows() |> 
  setNames(c("Plot type","Description")))
  }) |> 
  dplyr::bind_rows() |> 
  knitr::kable()
```
