---
title: "FreesearchR data report"
date: "Report generated `r gsub('(\\D)0', '\\1', format(Sys.time(), '%A, %d.%m.%Y'))`"
format: docx
author: FreesearchR data analysis tool
toc: false
params:
  data.file: NA
  version: NA
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# glue::glue("{format(lubridate::today(),'%A')}, {lubridate::day(lubridate::today())}.{lubridate::month(lubridate::today())}.{lubridate::year(lubridate::today())}")
```

```{r}
web_data <- readr::read_rds(file = params$data.file)
# web_data <- readr::read_rds(file = "~/FreesearchR/inst/apps/FreesearchR/www/web_data.rds")
library(gtsummary)
library(gt)

tbl_merge <- function(data) {
  if (is.null(names(data))) {
    data |> gtsummary::tbl_merge()
  } else {
    data |> gtsummary::tbl_merge(tab_spanner = names(data))
  }
}

vec2sentence <- function(data, sep.word = "and") {
  sep.word <- paste0(" ", gsub(" ", "", sep.word), " ")
  if (length(data) < 2) {
    out <- data
  } else if (length(data) == 2) {
    out <- paste(data, collapse = sep.word)
  } else {
    out <- paste(paste(data[-length(data)], collapse = ","), data[length(data)], sep = sep.word)
  }
  return(out)
}
```

## Introduction

Research should be free and open with easy access for all. The FreesearchR tool attempts to help lower the bar to participate in contributing to science by making guided data analysis easily accessible in the web-browser.

## Methods

Analyses were conducted using the *FreesearchR* data analysis web-tool version `r params$version` based on *R* version 4.4.1.

## Results

Below are the baseline characteristics.

```{r, results = 'asis'}
if ("table1" %in% names(web_data)) {
  tbl <- gtsummary::as_gt(web_data$table1)
  knitr::knit_print(tbl)
}
```

`r if (length(web_data$regression) > 0) glue::glue("Below are the results from the { tolower(vec2sentence(names(web_data$regression$regression$tables)))} {web_data$regression$regression$params$descr}.")`

```{r, results = 'asis'}
if ("regression" %in% names(web_data) && length(web_data$regression) > 0) {
  reg_tbl <- web_data$regression$regression$tables
  knitr::knit_print(tbl_merge(reg_tbl))
}
```

## Discussion

Good luck on your further work!
